---
title: "Accessibility"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(jplotexamples)
```


## 508 Compliance

The government has accessibility guidelines intended to ensure that electronic materials provided by the government are accessible. 

The EPA intranet site on 508 compliance is here: http://intranet.epa.gov/accessibility/index.html

Whole-government information is here: https://www.section508.gov/create/documents


## How to Evaluate a Document for Accessibility

From GSA: [Creating accessible digital products](https://www.section508.gov/create) (has sections for docx, pdf, pptx, software & websites, and spreadsheets)

- Website / html document
- pdf
- docx
- Interactive web app


## Steps To Take to Make a Typical Document Accessible

- Make sure images and figures have alternative text (would detailed captions fill this need?)
- Make sure visual elements are high-contrast, and distinguishable for those with colorblindness (`colorblindr` package?) (theme with white separating bars, etc?)




## Steps to Improving Accessibility in an R Document Pipeline


